text

### 2016-09-04 forgerard.tex
Keep on going with article

There is evidence that supports the expectation that one parameter in insufficient to describe the full range
of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations with differing $B_{max}-V_{max}$ identified by Si velocity.
\citet{2015MNRAS.451.1973S}
find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find on average values for $R_V \ll 3.1$,
much smaller than that of diffuse Milky Way dust, though the dispersion is large.
The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
the standard $R_V=3.1$ is recovered.

@@

Supernova-frame synthetic photometry is generated for the top-hat filter system
described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.

@@

We assume 
that  intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the Ca and Si spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ velocity $v_{Si}$:
these spectral features have been previously associated with SN~Ia diversity  
\citep{2006PASP..118..560B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2009A&A...500L..17B}.
Note that $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
A color-variation parameter $D$ describes further magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with (unknown) covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and distance errors introduced when normalizing the supernovae to be at a common distance.
The observed magnitudes are linearly dependent on an
extrinsic color-variation parameter $k$  parameter.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$; these have
been presented in \S\ref{data:sec}.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ v_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships between the spectral
features and intrinsic colors (encoded in $D$),  with intrinsic magnitudes.  The global parameters $\gamma$ are the slopes that connect the extrinsic colors
(encoded in $k$) and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 \ge 0, \delta_0\le0.
\end{equation}
The first two are imposed to constrain the definition of zero color (i.e. $E(B-V)=0$).    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\alpha_X/\alpha_2-1$
&
$   2.0^{   1.3}_{  -0.6}$
&
$   0.0^{   0.1}_{  -0.2}$
&
0
&
$   0.0^{   0.2}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.033^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.002}_{-0.002}$
&
$ 0.021^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
\\
$\beta_X/\beta_2-1$
&
$  0.26^{  0.05}_{ -0.05}$
&
$  0.00^{  0.03}_{ -0.03}$
&
0
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.25^{  0.03}_{ -0.03}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$\eta_X/\eta_2-1$
&
$  0.26^{  0.65}_{ -0.65}$
&
$ -0.09^{  0.53}_{ -0.55}$
&
0
&
$ -0.08^{  0.24}_{ -0.21}$
&
$ -0.57^{  0.51}_{ -0.59}$
\\
$\frac{\gamma_X}{\gamma_2}-1$
&
$  0.64^{  0.05}_{ -0.05}$
&
$  0.34^{  0.03}_{ -0.03}$
&
0
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_{X}$
&
$  4.87^{  0.48}_{ -0.43}$
&
$  3.96^{  0.40}_{ -0.35}$
&
$  2.96^{  0.31}_{ -0.28}$
&
$  2.29^{  0.26}_{ -0.23}$
&
$  1.64^{  0.21}_{ -0.19}$
\\
$\frac{\delta_X}{\delta_2}-1$
&
$-0.393^{ 0.182}_{-0.208}$
&
$-0.224^{ 0.101}_{-0.117}$
&
0
&
$-0.056^{ 0.051}_{-0.046}$
&
$-0.147^{ 0.096}_{-0.089}$
\\
$R_{\delta X}$
&
$ -2.70^{  1.32}_{ -2.44}$
&
$ -3.46^{  1.29}_{ -2.65}$
&
$ -4.46^{  1.43}_{ -3.11}$
&
$ -4.20^{  1.32}_{ -2.89}$
&
$ -3.80^{  1.20}_{ -2.61}$
\\
$\sigma_{X}$
&
$ 0.059^{ 0.012}_{-0.011}$
&
$ 0.031^{ 0.007}_{-0.007}$
&
$ 0.020^{ 0.004}_{-0.006}$
&
$ 0.013^{ 0.007}_{-0.008}$
&
$ 0.043^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% Intervals for Global Fit Parameters \label{global:tab}}
\end{table}

@@

The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
shows the expectation of the \citet{1999PASP..111...63F} dust model through its parameter $R^F_V$, plotted together with our measurements of
$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the effective wavelength of the supernova flux that passes
through the synthetic bands.
The $R_X$ are consistent with an  $R_V=2.5$.  The uncertainties in the 5 measurements
of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are consistent with $R_V=2.5$.

@@

The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
The range of $B-V$ colors is almost 4 times larger for the external contribution:
extreme colors can thus be attributed to the external source. 
Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of the contributions to color excess from external $E(B-V) =(\gamma_1-\gamma_2)k$ and
   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
   \label{ebv:fig}}
\end{figure}

The two separate color effects are conflated into a combined color excess with a single effective extinction behavior
\begin{equation}
R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}.
\end{equation}
The distribution for $R_{V,eff}$ for the supernovae in our sample is shown in Figure~\ref{rveff:fig}
and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ reproduced the original results, indicating that
the effective and true $R$ values are not separated by local posterior extrema.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/rveff.pdf}
   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
   for the supernovae in our sample.
   \label{rveff:fig}}
\end{figure}

The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail. 
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/Delta_hist.pdf} 
   \caption{Ideogram for the grey offset $\Delta$.
   \label{hist:fig}}
\end{figure}

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.
The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: selecting new Cholesky factors baased
on their distributions generally will not satisfy the condition of representing a correlation matrix.  
As a representation of a typical posterior draw of $C_c$ we present a matrix that element-by-element
is the mean of all covariance realizations.
For $UBVRI$ the matrix is
\begin{equation}
\begin{pmatrix}
0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
 \end{pmatrix} \text{mag}^2.
 \end{equation}
Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
be expressed as having standard deviations $(0.066 , 0.033 , 0.022 , 0.050)$ mag with
 correlations
 \begin{equation}
\begin{pmatrix}
1.000 & 0.634 & -0.256 & -0.300 \\
0.634 & 1.000 & -0.203 & 0.032 \\
-0.256 & -0.203 & 1.000 & 0.604 \\
-0.300 & 0.032 & 0.604 & 1.000
  \end{pmatrix}.
 \end{equation}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: the distributions (for all Monte Carlo chain links for all supernovae) are shown in Figure~\ref{perobject:fig}.
There is a core distribution within the supernova parameter-space, with around ten objects that live on the outskirts of that
distribution.  Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
Otherwise the distribution in $EW_{Ca}$--$v_{Si}$ space is the view that
shows the most outliers.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are shown in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
$EW_{Si}$--$v_{Si}$, which are statistics both associated with SiII.
External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.

@@

SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits colors that are inconsistent with low $R_V<2.0$.
It is spectroscopically normal, having a spectral evolution similar to SN~2011fe (though SN~2014J does show
overall higher photospheric velocities).  As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
for the measurement of color excess nulling out the effects of Ca and Si equivalent width.  SN~2014J is not part of the SNfactory
sample.

We take the color excesses  in $UBRi$  relative to $V$
of \citet{2014ApJ...788L..21A}, following their prescription of taking the average of data within 5-days of peak $B$ magnitude.

[ 2.55835177 -1.57193957] [[ 0.05797162  0.05911801]
 [ 0.05911801  0.20369998]]

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
   \caption{
   \label{sn2014j:fig}}
\end{figure}

\section{Discussion}
\label{discussion:sec}
The model favors spectral features as indicating supernova magnitude and color, and the existence of an internal supernova parameter
that affects colors, in addition to external (dust) colors.

The extrinsic dust gives $R^F_V=2.5$. Intrinsic cannot be associated with dust.

>>>>

There is evidence that supports the expectation that one parameter in insufficient to describe the full range
of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations with differing $B_{max}-V_{max}$ identified by Si velocity.
\citet{2015MNRAS.451.1973S}
find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find on average values for $R_V \ll 3.1$,
much smaller than that of diffuse Milky Way dust, though the dispersion is large.
The also confirm the \citet{2011ApJ...729...55F} finding hat low $R_V$ is associated with high-extinction supernovae.
The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
the standard $R_V=3.1$ is recovered.

@@

Supernova-frame synthetic photometry is generated for the top-hat filter system
described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
For  SiII$\lambda 6355$ the weighted mean from phases within 3 days of maximum light is used.
(What is done for EW?)

@@

We assume 
that  intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the Ca and Si spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ velocity $v_{Si}$:
these spectral features have been previously associated with SN~Ia diversity  
\citep{2006PASP..118..560B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2009A&A...500L..17B}.
Note that $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
A color-variation parameter $D$ describes further magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with (unknown) covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and distance errors introduced when normalizing the supernovae to be at a common distance.
The observed magnitudes are linearly dependent on an
extrinsic color-variation parameter $k$  parameter.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$; these have
been presented in \S\ref{data:sec}.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ v_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships between the spectral
features and intrinsic colors (encoded in $D$),  with intrinsic magnitudes.  The global parameters $\gamma$ are the slopes that connect the extrinsic colors
(encoded in $k$) and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
\end{equation}
The first two are imposed to constrain the definition of zero color (i.e. $E(B-V)=0$).    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$.
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other,
as confirmed after recalculation of the posterior with exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
The $\delta$ and $\gamma$ values of a single run cannot definitively be attributed as being intrinsic or extrinsic; we break the degeneracy
by assigning the parameter whose values that are more consistent with dust as $\gamma$ and the other parameter as $\delta$.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\alpha_X/\alpha_2-1$
&
$   2.0^{   1.3}_{  -0.6}$
&
$   0.0^{   0.1}_{  -0.2}$
&
0
&
$   0.0^{   0.2}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.033^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.002}_{-0.002}$
&
$ 0.021^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
\\
$\beta_X/\beta_2-1$
&
$  0.26^{  0.05}_{ -0.05}$
&
$  0.00^{  0.03}_{ -0.03}$
&
0
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.25^{  0.03}_{ -0.03}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$\eta_X/\eta_2-1$
&
$  0.26^{  0.65}_{ -0.65}$
&
$ -0.09^{  0.53}_{ -0.55}$
&
0
&
$ -0.08^{  0.24}_{ -0.21}$
&
$ -0.57^{  0.51}_{ -0.59}$
\\
$\gamma_X/\gamma_2-1$
&
$  0.64^{  0.05}_{ -0.05}$
&
$  0.34^{  0.03}_{ -0.03}$
&
0
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_{X}$
&
$  4.87^{  0.48}_{ -0.43}$
&
$  3.96^{  0.40}_{ -0.35}$
&
$  2.96^{  0.31}_{ -0.28}$
&
$  2.29^{  0.26}_{ -0.23}$
&
$  1.64^{  0.21}_{ -0.19}$
\\
$\delta_X/\delta_2-1$
&
$-0.393^{ 0.182}_{-0.208}$
&
$-0.224^{ 0.101}_{-0.117}$
&
0
&
$-0.056^{ 0.051}_{-0.046}$
&
$-0.147^{ 0.096}_{-0.089}$
\\
$R_{\delta X}$
&
$ -2.70^{  1.32}_{ -2.44}$
&
$ -3.46^{  1.29}_{ -2.65}$
&
$ -4.46^{  1.43}_{ -3.11}$
&
$ -4.20^{  1.32}_{ -2.89}$
&
$ -3.80^{  1.20}_{ -2.61}$
\\
$\sigma_{X}$
&
$ 0.059^{ 0.012}_{-0.011}$
&
$ 0.031^{ 0.007}_{-0.007}$
&
$ 0.020^{ 0.004}_{-0.006}$
&
$ 0.013^{ 0.007}_{-0.008}$
&
$ 0.043^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% Intervals for Global Fit Parameters \label{global:tab}}
\end{table}

@@

The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
shows the expectation of the \citet{1999PASP..111...63F} dust model through its parameter $R^F_V$, plotted together with our measurements of
$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the effective wavelength of the supernova flux that passes
through the synthetic bands.
The $R_X$ are consistent with an  $R^F_V=2.5$.  The uncertainties in the 5 measurements
of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are also consistent with $R^F_V=2.5$.

@@

The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
 $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
Recall that given our boundary conditions the means of both distributions are equal to zero. 
The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
The range of $B-V$ colors is $\sim 4$ times larger for the external contribution:
extreme colors can thus be attributed to the external source. 
Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Histograms of the contributions to color excess from external $E(B-V) =(\gamma_1-\gamma_2)k$ and
   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
   \label{ebv:fig}}
\end{figure}

The two separate color effects are conflated into a combined color excess with a single effective total-to-selective extinction
\begin{equation}
R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}.
\label{RVeff:eqn}
\end{equation}
The distribution for $R_{V,eff}$ for the supernovae in our sample is shown in Figure~\ref{rveff:fig}
and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ 
and $\delta=0$ (technically $\delta_0 = -\epsilon$ due to the $\delta_0<0$ condition)
reproduces the original results, indicating that
the effective and true $R$ values are not separated by local posterior extrema.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/rveff.pdf}
   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
   for the supernovae in our sample.
   \label{rveff:fig}}
\end{figure}

The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail in the positive (fainter) direction.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/Delta_hist.pdf} 
   \caption{Ideogram for the grey offset $\Delta$.
   \label{hist:fig}}
\end{figure}

Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.
The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: assembling
a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
chain, element by element.
For $UBVRI$ the matrix is
\begin{equation}
\begin{pmatrix}
0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
 \end{pmatrix} \text{mag}^2.
 \end{equation}
Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
be expressed as having standard deviations and
 correlations
 \begin{equation}
 \begin{pmatrix}
0.066 , 0.033 , 0.022 , 0.050 
  \end{pmatrix} \text{mag}
 \label{color_sd:eqn}
   \end{equation}
 \begin{equation}
\begin{pmatrix}
1.000 & 0.634 & -0.256 & -0.300 \\
0.634 & 1.000 & -0.203 & 0.032 \\
-0.256 & -0.203 & 1.000 & 0.604 \\
-0.300 & 0.032 & 0.604 & 1.000
  \end{pmatrix}.
  \label{color_cor:eqn}
 \end{equation}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
Outliers in  $EW_{Ca}$--$v_{Si}$ parameters are also clearly distinguished.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are given in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
$EW_{Si}$--$v_{Si}$.
External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.

@@

SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits a low $R_V<2.0$.
It is spectroscopically normal, having a spectral evolution similar to SN~2011fe.
As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
for the measurement of color excess, nulling out the effects of Ca and Si equivalent width.
SN~2014J does show
overall higher photospheric velocities than SN~2011fe, but the results in \S\ref{results:sec} show that this is unimportant.
Note that SN~2014J is not part of the data sample described in \S\ref{data:sec}.

Data of SN~2014J are now analyzed using our model and the training with the SNfactory sample.
The data are the color excesses  in $UBRi$  relative to $V$ at peak brightness  taken from \citet{2014ApJ...788L..21A}
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E^o(U-V) =   2.23 \pm   0.03$,
$E^o(B-V) =   1.28 \pm   0.04$,
$E^o(R-V) =  -0.47 \pm   0.03$,
$E^o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
These data are fit to the model
\begin{equation}
E^o(X-V) =  \left(\frac{\gamma_X}{\gamma_2}-1\right)k +  \left(\frac{\delta_X}{\delta_2}-1\right)D,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.
